---
title: "Analysing interactions between beet's rootsystem and nematodes"
author: "Artur Freeman & Tom Kenda"
date: '`r format(Sys.time(), "%B %d, %Y,%H:%M")`'
output:
  html_document: # options pour la mise en page des sortie HTML
    smart: FALSE
    code_folding: hide #  Cache le code  
    collapsed: yes # Crée un document unique 
    fig_caption: yes # Figures encapsulées ? 
    fig_height: 5 # Hauteur par défaut des figures
    fig_width: 6 # Largeur par défaut des figures
    highlight: tango # Style de mise en valeur du code
    number_sections: no # Ajout table des matières 
    theme: united  # Style du document
    toc: yes # Table des matiere ?
    toc_depth: 3  # Profondeur table des matières
    toc_float: yes # Table des matières flottante
editor_options: 
  chunk_output_type: console
---

########################################################################
# 1 : SET UP
########################################################################

```{r setup, include=FALSE}

# Options générales des blocs de code R
knitr::opts_chunk$set(comment="")
knitr::opts_chunk$set(warning = FALSE)

### List of packages to load

# default packages for CRootBox
library(tidyverse)
library(plyr)
library(readr)
library(data.table)
library(dplyr)
library(Matrix)

# extra packages for our project
require(readxl)
require(pander)
panderOptions('knitr.auto.asis', FALSE)
require(car)
require(Hmisc)
require(EnvStats)
require(emmeans)
require(visreg)
require(sjplot)
require(FactoMineR)
require(factoextra)
require(ggplot2)
require(NbClust)
require(lubridate)
library(reshape2)

# in cas we have so solve ode
# library(deSolve)
```

```{r , include=FALSE}
#### Working directory and source functions

# Tom
setwd("/Users/tomk-/OneDrive - UCL/My UCL/LBRAI2219 - Modélisation biologique/crootbox/crootbox")
source("inputs/io_function.R") # CROOTBOX function

# Artur
# setwd("C:/Users/artur/OneDrive/Documents/smartroot/crootbox")
# source("C:/Users/artur/OneDrive/Documents/smartroot/crootbox/inputs/io_function.R") # CROOTBOX

```

*When using CRootBox for the first time you should also run this :*

The code should compile with any c++11 compiler, e.g. for g++: MinGW has been tested. Then create a new system environment variable. Path --> `C:\MinGW\bin`

```{r}

# Open the terminal:
#   cd ~/GitHub/marshal-pipeline/17_06 CRootBox
# 
# FOR MAC AND LINUX
# g++ *.cpp -std=c++11 -o crootbox.out   
# crootbox.out   
#
#
# FOR WINDOWS
# g++ *.cpp -std=c++11 -o crootbox.exe   
# crootbox.exe


# Custom functions
# source("inputs/io_function.R") # CROOTBOX

# Update the crootbox executable file
# MAC
# file.copy("inputs/crootbox_source/crootbox.out", 
#           "inputs/crootbox.out", 
#           overwrite = T)
# WINDOWS
# file.copy("inputs/crootbox_source/crootbox.exe", 
#           "inputs/crootbox.exe", 
#           overwrite = T)
```

########################################################################
# 2 : SET THE SIMULATION PARAMETERS & RUN CROOTBOX
########################################################################

Note : a detailled list of the parameters can be found in the following article (namely in table 2 and 3 ) 

    *Andrea Schnepf, Daniel Leitner, Magdalena Landl, Guillaume Lobet, Trung Hieu Mai, Shehan Morandage, Cheng Sheng, Mirjam Zörner, Jan Vanderborght, Harry Vereecken, CRootBox: a structural–functional modelling framework for root systems, Annals of Botany, Volume 121, Issue 5, 18 April 2018, Pages 1033–1053, https://doi.org/10.1093/aob/mcx221*

Some parameters were found using the SmaartRoot software (integrated in ImageJ, see source below) combined with beet root scans. For some other parameter we could not find any information in the litterature and thus we had to set them arbitrarly. 

    *A Novel Image Analysis Toolbox Enabling Quantitative Analysis of Root System Architecture. Guillaume Lobet, Loic Pages and Xavier Draye, 2011*

```{r crootbox1}
# CROOTBOX PARAMETERS

### A. We load the default parameter sets for the simulation 
rparam <- read_rparam(path = "inputs/param_default.rparam") 
pparam <- read_pparam(path = "inputs/param_default.pparam")

### B. Define the parameter
    
## B.1. We store the input parameters into 'easy-to-understand' variables

# - - - - - - - - - - - ### unit   ### source

## Plant param
simulation_time <- 200  # [days]
planting_depth <- 3     # [cm]  (Romaneckas et al., 2009)
maxB <- 0               # [1]   (Weaver and Bruner, 1927) no basal root for beet

## Root param     nb: a=radius, vitesseP=initial elong. rate
# Type 1 : Pivot          
a_1 <- 0.129              # [cm]      littérature https://doi.org/10.3390/agriculture11010021
vitesseP_1 <- 1.7621349   #[cm/jour] < smartroot
lb_1 <- 2                 # [cm]      < arbitraire
la_1 <- 12                # [cm]      < arbitraire
ln_1<- 1.6031327          # [cm]      < Smartroot
lmax_1 <- 300             # [cm]      littérature https://doi.org/10.1080/14620316.2006.11512146
succ_val1_1 <- 2          # Nombre de successeurs sur taproot
succ_val2_1 <- 2          # Type du successeur 1
succ_val3_1 <- 3          # Type du successeur 2
succP_val1_1 <- 2         # Nombre de successeurs sur taproot = succ_val1_1
succP_val2_1 <- 0.33      # probability  (Weaver and Bruner, 1927) 
succP_val3_1 <- 0.66      # probability  (Weaver and Bruner, 1927)

# à vérifié !! --> (Weaver and Bruner, 1927)
# inversé long lateral et latéral normal ? car taille pas logique ?


# TYPE 2: Lateral (short)
a_2 <- 0.10               # [cm]      (Weaver and Bruner, 1927) 
vitesseP_2 <- 0.3802029   # [cm/jour] < Smartroot 
lmax_2 <- 7.0             # [cm]      (Weaver and Bruner, 1927)
sigma_tropism_2 <- 0.2    # ?? !!!!


# TYPE 3 : Longue lateral
a_3 <- 0.10               # [cm]      (Weaver and Bruner, 1927) 
vitesseP_3 <- 0.75        # [cm/jour] < Smartroot 
lmax_3 <- 240             # [cm]      (Weaver and Bruner, 1927)
sigma_tropism_3 <- 0.2  


#### B.2. we store all parameter in the rparam and pparam file

launch_simulation <- function(simulation_time=20){
  ## function to launch the simulation : 
  ## 1. store parameter defined in the global env. in the P and R param file
  ## 2. run CRootBox
  ## 3. return the current rootsystem as a dataframe
  
 # Global parameters - PParam
 pparam$val1[pparam$param == "simtime"] <- simulation_time
 pparam$val1[pparam$param == "plantingdepth"] <- planting_depth
 pparam$val1[pparam$param == "maxB"] <- maxB
 
 # Type 1 : Pivot 
 rparam$val1[rparam$name == "Taproot" & rparam$param == "a"] <-   a_1 
 rparam$val1[rparam$name == "Taproot" & rparam$param == "r"] <-   vitesseP_1
 rparam$val1[rparam$name == "Taproot" & rparam$param == "lb"] <-  lb_1
 rparam$val1[rparam$name == "Taproot" & rparam$param == "la"] <-  la_1
 rparam$val1[rparam$name == "Taproot" & rparam$param == "lmax"]<- lmax_1
 rparam$val1[rparam$name == "Taproot" & rparam$param == "ln"] <-  ln_1
 
 rparam$val1[rparam$name == "Taproot" & rparam$param == "successors"] <- succ_val1_1
 rparam$val2[rparam$name == "Taproot" & rparam$param == "successors"] <- succ_val2_1
 rparam$val3[rparam$name == "Taproot" & rparam$param == "successors"] <- succ_val3_1
 rparam$val1[rparam$name == "Taproot" & rparam$param == "successorP"] <- succP_val1_1
 rparam$val2[rparam$name == "Taproot" & rparam$param == "successorP"] <- succP_val2_1
 rparam$val3[rparam$name == "Taproot" & rparam$param == "successorP"] <- succP_val3_1
 
 #TYPE 2: Lateral
 rparam$val1[rparam$name == "Lateral" & rparam$param == "a"] <-   a_2
 rparam$val1[rparam$name == "Lateral" & rparam$param == "r"] <-   vitesseP_2
 rparam$val1[rparam$name == "Lateral" & rparam$param == "lmax"] <- lmax_2
 
 #TYPE 3 : Longue lateral
 rparam$val1[rparam$name == "LongLateral" & rparam$param == "a"] <-   a_3
 rparam$val1[rparam$name == "LongLateral" & rparam$param == "r"] <-   vitesseP_3
 rparam$val1[rparam$name == "LongLateral" & rparam$param == "lmax"] <- lmax_3
 
 # update the input text files 
 write_rparam(rparam, "inputs/param.rparam")
 write_pparam(pparam, "inputs/param.pparam")

 ### Run crootbox ###
 system("inputs/crootbox.exe") # Run crootbox for windows

 # Load the simulated data into R to process it and to store it for further use
 current_rootsystem <- fread("outputs/current_rootsystem.txt", header = T)

 return(current_rootsystem)
}

# C. We create variables that will contain the 
# results of our crootbox simulations
all_rootsystems <- NULL
all_totlength <- NULL
n_tot_simulation <- 1
n_cr_sim <- 0

current_rootsystem <- launch_simulation(simulation_time = 200)

```

########################################################################
# 3 : EXTRACT DATA FROM ROOTSYSTEM 
########################################################################

This part is useful only if we loop and create many root system - see later (section 8)

```{r}

# We enrich the root system simulation data with metadata
# This is needed to find back the information in the large data file 
# at the end of the simulations
current_rootsystem <- current_rootsystem %>% 
                      mutate(vitesse_primaire = vitesseP_1, 
                             vitesse_secondaire = vitesseP_2,
                             densite_lat = ln_1,
                             simulation_id = n_cr_sim)

# We create a table with all the root systems
all_rootsystems <- rbind(all_rootsystems, current_rootsystem)

# We store the root system simulation with a unique name
write_csv(current_rootsystem, 
          paste0("outputs/rootsystems/rootsystem_",vitesseP_1,
                 "_",vitesseP_2,
                 "_",ln_1,
                 ".csv")) 

# OPTIONAL
# extract the root length density from the simulation data
# The idead here is, if needed, to store only the relevant info
# out of our simulation run and discard the rest

totlength <- data.frame(vitesse_primaire = vitesseP_1, 
                        vitesse_secondaire = vitesseP_2,
                        densite_lateral = ln_1,
                        simulation_id = n_cr_sim, 
                        total_length = sum(current_rootsystem$length), 
                        n_root = length(unique(current_rootsystem$branchID)))

# We store in a data frame the rld from all the simulations
all_totlength <- rbind(all_totlength, totlength)

```


########################################################################
# 4 : PLOT THE ROOT SYSTEM
########################################################################


```{r crootbox}
# Root system from the side
plot_current_root_S <- function(current_rootsystem){
  # cat("Plot of the root system from the side ")
  current_rootsystem %>%
    ggplot() +
    theme_classic() +
    geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2, colour=time), 
                 alpha=0.9)+
    scale_colour_gradientn(colours = terrain.colors(10)) +
    coord_fixed()
}

# Root system from above
cat("Plot of the root system from below/above")
current_rootsystem %>%
  ggplot() +
  theme_classic() +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, colour = time), alpha=0.9) +
  scale_colour_gradientn(colours = terrain.colors(10)) +
  coord_fixed()

plot_current_root_S(current_rootsystem)

```

########################################################################
# 5 : Get the root volume for each time step and each soil layer
########################################################################

We created 2 functions here : the first one to extract the root volume (RV) in each layer of soil and the second one to plot it. This will be used to model the nematode population later on.

```{r}

root_volume <- function(current_rootsystem, max_depth=300, layer_width=50, round=4){
  # function that take root system as a dataframe (containing at least the time, volume, 
  # length and depth (z2) of each root segment) then compute the lateral root volume for
  # each soil layer from 0 cm to max_depth (cm) with a layer width of 'layer_width'
  
  # calculate the volume of each root segment (assuming this is cylinder pi * r² * l) in cm³ ?
  current_rootsystem$volume <- pi * current_rootsystem$radius**2 * current_rootsystem$length 
  
  # Get a vector with the depth of the layers
  d <- 0
  depth_list <- NULL
  while(d > -max_depth){
    depth_list <- c( depth_list, d )
    d <- d - layer_width
  }
  #cat("\n depth_list : ", depth_list)
  
  # initialize the dataframe to store result of RV
  simulation_time <- max(current_rootsystem$time)
  RV <- setNames(data.frame(matrix(ncol = length(depth_list), nrow = simulation_time)), depth_list)
  
  # loop over time and depth
  
  for(ti in 1:nrow( RV )) {      # for timestep i
    rootsystem_Ti <- current_rootsystem[ current_rootsystem$time <= ti ]
    
    for(depth in depth_list) {    # for depth i
      rootsystem_Ti_Di <- rootsystem_Ti[ rootsystem_Ti$z2 > (depth - layer_width) & rootsystem_Ti$z2 <= depth ]
      
      RV[ti, toString(depth)] <- round(sum(rootsystem_Ti_Di$volume), round)
      
    }
  }
  # return the dataframe with the RV
  RV
}

# test
RV <- root_volume(current_rootsystem, 100, 20)
RV

plot_RV <- function(RV, line_width=1){
  # function that plot the lateral root volume for each soil layer
  # input : RV , a df containing one colunm for each soil layer 
  # output : ggplot graph
  
  # add a vector time to reshape/melt the DF
  time <- data.frame("time"= c(0:nrow(RV)))
  RV <- rbind(c(0), RV) # just add the (0,0) to each layer
  RV_time <- cbind(time, RV)
  # melt in 3 columns
  RV_long <- melt(RV_time, id="time", variable.name = "depth" ) 
  
  # plot
  RV_plot <- ggplot(RV_long,            
                     aes(x = time,
                         y = value,
                         color = depth)) +  geom_line(size=line_width) +
    labs(y="Root volume (cm³)", x="Time (days)", color="Depth (cm)")

  # return the plot
  RV_plot
}

# testing the 2 functions :
RV <- root_volume(current_rootsystem, 250, 50)
plot_RV(RV)
```


########################################################################
# 6.  Build the model for nematode development 
########################################################################

## Modeling soil temperature

We determined an equation to simulate the soil temperature at different depths for different soil types (described in 'temperature model.pdf'). This temperature is a key parameter for the development of nematodes in the soil.

```{r loaddata}

# optimum parameters of the thermal wave : 
# beta1: average, beta2: amplitude, beta3: phase shift
beta_opti <- c(10.26, 7.238, -1.973)

#alpha <- 0.015 # thermal diffusivity of the soil, here wet clay

soiltemp <- function(depth, alpha, timerange, beta_opti = beta_opti) {
  beta_opti[1] +  
    beta_opti[2] *  
        (exp(-depth*sqrt(pi/(alpha*365)))) * 
        cos( (((2*pi*timerange)/365)) - depth*sqrt(pi/((alpha)*365)) - beta_opti[3] )
}

```

## Modelling nematod polulation according to soil t° and root volume


I put together the 2 bocs of the model: the soil temperature model, and the model that takes this development cycle to model the interaction of the nematodes.

If the temperatures are below the development threshold (here 11°C), the model considers that the population does not develop and therefore remains constant. If temperatures are above the threshold, the population starts to grow. 

**test avec un sol argileux humide à 10cm de profondeur**

### Logistic function

```{r}
logistic <- function(t, r, K, N0) {
  K * N0 * exp(r * t) / (K + N0 * (exp(r * t) - 1))
}

plot(0:100, logistic(t=0:100, r=0.1, K=10, N0=0.1), main='Logistic normal')
```

### r-Factor function

The relationship between growth rate and temperature is approximately linear. (source : https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4755701/)

```{r}

getRFactor <-function(Temperature, TempOpti=25, TempSEuil=11,TempMax=38 ){
  #tempseuil : 11°C pour Heterodera Schachtii
  #tempOpt : 25 °C environ
  #tempMax : 38°C environ.
  
  if(Temperature < TempOpti && Temperature >= TempSEuil){
    r_factor <- (Temperature - TempSEuil) / (TempOpti - TempSEuil)
  }
  
  else if (Temperature >=TempOpti && Temperature <= TempMax) {
    r_factor <- 1-((Temperature-TempOpti)/(TempMax-TempOpti))
  } 
  else {r_factor <- 0}
  
  return(r_factor)
}

# test & visualize
t <- c(1:45)
r_factor <- t*0
for(i in t){
  r_factor[i] <- getRFactor(i)
}
plot(t, r_factor, main="r-factor evoluation", ylab = "r-factor [-]", xlab = "Temperature [°C]" )

```

### Model function

```{r temperatures et nématodes}

modele <- function(depth_m, alpha, planting_day, seuil,  Pop_init, RV_layer_i, 
                   K_pot, r_max=0.07) {
  ## SPEC. : depth  should be given in absolute value and in meters
  
  ## r_max <- 0.07 approximately the maximum growing rate for a population ~ the max
  ## slope of the curve according to in situ data
  ##  r = r_max * r_factor and r_factor = 1 when temp° is optimal

  time_range <- c(planting_day:(planting_day+nrow(RV_layer_i)-1))
   
  pop <- rep(Pop_init,length(time_range))
  
  tempSim <- soiltemp(depth_m, alpha, time_range, beta_opti)

  K <- RV_layer_i * K_pot 

  for (i in c(2:(length(time_range))) ){
    
    if (tempSim[i]> seuil && K[i,] > 0) {   
       
      ri <- r_max * getRFactor(tempSim[i])
      
      pop[i] <- logistic(1 , r = ri, K = K[i,], N0 = pop[i-1] )
    }
    else {pop[i] = pop[i-1]}
  }
  return(pop)
}

modele(depth_m = 0.1, alpha = 0.015, planting_day = 90, seuil = 11, Pop_init = 10,
      RV_layer_i = RV[1], K_pot = 100, r_max=0.05)

```

########################################################################
# 7.  Combining all models and equations 
########################################################################

*Nematode population function*

```{r}
Nematode_population <- function(RV, model_fun, PopNem_init,  alpha , planting_day, 
                                  seuil, K_pot, r_max  ){
  ## take a dataframe of rootvolume and the function to compute the nematode population,
  ## then it compute the nematode population for each soil layer.
  
  depth_list <- strtoi(names(RV))
  half_layer_size <- (depth_list[2] - depth_list[1])/2
  depth_list <- depth_list + half_layer_size
  
  # initialize the dataframe to store result of RV
  simulation_time <- nrow(RV)
  PopNem <- setNames(data.frame(matrix(ncol = length(depth_list), nrow = simulation_time)),
                     depth_list)
  
  for(i in c(1:ncol(RV))){ # loop over each soil layer
    
    d <- depth_list[i] * -1 / 100 # the soil temp model is in absolute value and in meters (not cm)
    
    PopNem[,i] <- model_fun(depth_m = d, alpha = alpha, planting_day = planting_day , 
                            seuil = seuil, K_pot=K_pot, r_max=r_max,
                            Pop_init = PopNem_init[i], RV_layer_i=RV[i] )
                          # note : RV[,i] is the RV for soil layer i for every timestep
  }
  # return the df with Pop°
  return(PopNem)
}

```

**Plot nematode population**

```{r}

plot_PopNem <- function(PopNem, total=FALSE, line_width=1){
  # function that plot the nematode population for each soil layer
  # input : PopNem , a df containing one colunm for each soil layer 
  # output : ggplot graph, if total is True, add a col. with total pop.
  
  if(total){
    PopNem["Total"] <- rowSums(PopNem, na.rm = T)
  }  
  
  # add a vector time to reshape/melt the DF
  time <- data.frame("time"= c(1:nrow(PopNem)))
  PopNem_time <- cbind(time, PopNem)

  # melt in 3 columns
  PopNem_long <- melt(PopNem_time, id="time", variable.name = "depth" ) 
  
  # plot
  PopNem_plot <- ggplot(PopNem_long,            
                     aes(x = time,
                         y = value,
                         color = depth)) +  geom_line(size=line_width) +
    labs(y="Number of nematodes", x="Time (days from planting date)", color="Depth (cm)")+
    expand_limits(x = 0, y = 0)

  # return the plot
  return(PopNem_plot)
}

# test
PopNem <- Nematode_population(RV, modele, PopNem_init = c(20, 12, 10, 7, 1),  alpha = 0.015,
                              planting_day = 90, seuil = 11, K_pot=500, r_max = 0.07)

plot_PopNem(PopNem, T)

```


### All from the beginning

```{r}
# launch simulation
current_rootsystem <- launch_simulation(simulation_time = 200)

# root volume
RV <- root_volume(current_rootsystem, 200, 50)

print(paste("You should have", ncol(RV), "value of initial population !"))

# initial population of nematode in each layer of soil
PopNem_init = c(10, 8, 7, 5)

# model the nem. population
PopNem <- Nematode_population(RV, modele, PopNem_init,  alpha = 0.015, planting_day = 90, 
                              seuil = 11, K_pot=500, r_max = 0.07)

# plot Root and Nem
plot_RV(RV)
plot_PopNem(PopNem, T)
plot_current_root_S(current_rootsystem)

```

########################################################################
# 8.  CHANGING THE ROOT ARCHITECTURE TO SEE THE INFLUENCE ON NEMATODE 
########################################################################

In this section we decided to see the effect of `ln_1` (the lateral density on the taproot) and `lmax_3` (the maximum length of the long-lateral roots) on the nematode population. We will change their value in a certain range separately and then together. 

First we define another function to make our calculation easier :

## Function simulation_2

```{r}
launch_simulation2 <- function(simulation_time = 200, ln_1 = 1.6, lmax_3 =  240){
  ## function to launch the simulation (only changing relevant param): 
  ## 1. store parameter defined in the global env. in the P and R param file
  ## 2. run CRootBox
  ## 3. return the current rootsystem as a dataframe
  
 # Parameters relevant for that simulation
 pparam$val1[pparam$param == "simtime"] <- simulation_time
 rparam$val1[rparam$name == "Taproot" & rparam$param == "ln"] <-  ln_1
 rparam$val1[rparam$name == "LongLateral" & rparam$param == "lmax"] <- lmax_3
 
 # update the input text files 
 write_rparam(rparam, "inputs/param.rparam")
 write_pparam(pparam, "inputs/param.pparam")

 ### Run crootbox ###
 system("inputs/crootbox.exe") # Run crootbox for windows

 # Load the simulated data into R to process it and to store it for further use
 current_rootsystem <- fread("outputs/current_rootsystem.txt", header = T)

 return(current_rootsystem)
}

```

## Changing `ln_1` parameter only

```{r}
# Define param values
ln1_vec <-  c( 1 , 1.6 ,  3.1 ,  4.6 ) 
lmax_3 <- 170

# empty df for storing results
Nematode_df <- setNames(data.frame(matrix(ncol = 1, nrow = simulation_time)), 'Time')
Nematode_df['Time'] <- c(1:simulation_time)

final_pop <- NULL
all_rootsystems <- NULL
all_totlength <- NULL
n_tot_simulation <- length(ln1_vec)
n_cr_sim <- 0
n_rep <- 10

# initial population of nematode in each layer of soil
PopNem_init = c(20, 12, 10, 7, 1) # approx 50 nematodes in the beginning ~(Werf et al., 1986)

### loop over param ###
for (ln_1 in ln1_vec){
  # Output the advancement in the simulation
  n_cr_sim <- n_cr_sim + 1
      
  for(i in c(1:n_rep)){    
    print(paste0(n_cr_sim, " / ", n_tot_simulation, " crootbox sims || Rep - ", i))
    
    # assign new value to the param & run
    current_rootsystem <- launch_simulation2(ln_1 = ln_1, lmax_3 = lmax_3)
    
    # root volume
    RV <- root_volume(current_rootsystem, 250, 50)
    
    # model the nem. population
    PopNem <- Nematode_population(RV, modele, PopNem_init,  alpha = 0.015, planting_day = 90, 
                                  seuil = 11, K_pot=500, r_max = 0.07)
    # Store total population
    Nematode_df[, "total_pop"] <-rowSums(PopNem, na.rm = T)
    
    final_pop <- rbind(final_pop, Nematode_df[simulation_time,]%>%
                                    mutate(ln_1 = ln_1, lmax_3 = lmax_3)
                       )
  }
  
  #####    
      # We enrich the root system simulation data with metadata
      current_rootsystem <- current_rootsystem %>% 
                            mutate(ln_1 = ln_1, lmax_3 = lmax_3)
      
      # We create a table with all the root systems
      all_rootsystems <- rbind(all_rootsystems, current_rootsystem)
      
      # # We store the root system simulation with a unique name
      # write_csv(current_rootsystem, 
      #           paste0("outputs/rootsystems/rootsystem_",vp,
      #                  "_",vs,
      #                  "_",ln,
      #                  ".csv"))  
      
      # extract the root length density from the simulation data
      totlength <- data.frame(ln_1 = ln_1, lmax_3 = lmax_3,
                              simulation_id = n_cr_sim, 
                              total_length = sum(current_rootsystem$length), 
                              n_root = length(unique(current_rootsystem$branchID)))
      
      # We store in a data frame the rld from all the simulations
      all_totlength <- rbind(all_totlength, totlength)
  ###
  
  # plot Root and Nem
  print( plot_RV(RV)+ 
           ggtitle(paste0('RootVol (ln_1 = ',ln_1, ', lmax_3 = ',lmax_3,')'))  )
  print( plot_PopNem(PopNem, T) + 
           ggtitle(paste0('PopNem (ln_1 = ',ln_1, ', lmax_3 = ',lmax_3,')')) )

}

  print( plot_current_root_S(current_rootsystem) +
           ggtitle(paste0('Rootsystem (ln_1 = ',ln_1, ')') ) )
```

### Compare the rootsystem

```{r}
# final result :
final_pop$ln_1 <- as.factor(final_pop$ln_1)

### boxplot
ggplot(final_pop, aes(x=ln_1, y=total_pop) ) + 
  geom_boxplot( fill="green", alpha=0.5)+ 
  ylab("Final nematode population")+ xlab("Lateral density (cm)")

  
# Everything on the same plot
df <- melt(Nematode_df, id.vars="Time")
ggplot(df, aes(Time,value, col=variable)) + geom_point() +
        ylab("Nematode population [individuals]") + xlab("Time [days]")

all_totlength %>% 
  ggplot(aes(ln_1, total_length, 
             colour = factor(lmax_3))) +
  geom_line() + 
  theme_bw()

```


## Changing `lmax_3` parameter only

```{r}
# Define param values
lmax3_vec <- c( 30 , 90 , 170 , 250)
ln_1 <- 1.6

# empty df for storing results
Nematode_df <- setNames(data.frame(matrix(ncol = 1, nrow = simulation_time)), 'Time')
Nematode_df['Time'] <- c(1:simulation_time)

final_pop <- NULL
all_rootsystems <- NULL
all_totlength <- NULL
n_tot_simulation <- length(lmax3_vec) # * length(ln1_vec)
n_cr_sim <- 0
n_rep <- 10

# initial population of nematode in each layer of soil
PopNem_init = c(20, 12, 10, 7, 1) # approx 50 nematodes in the beginning ~(Werf et al., 1986)

### loop over param ###
for (lmax_3 in lmax3_vec){
      # Output the advancement in the simulation
      n_cr_sim <- n_cr_sim + 1
      
  for(i in c(1:n_rep)){    
    print(paste0(n_cr_sim, " / ", n_tot_simulation, " crootbox sims || Rep - ", i))
    
    # assign new value to the param & run
    current_rootsystem <- launch_simulation2(lmax_3 = lmax_3, ln_1 = ln_1)
    
    # root volume
    RV <- root_volume(current_rootsystem, 250, 50)
    
    # model the nem. population
    PopNem <- Nematode_population(RV, modele, PopNem_init,  alpha = 0.015, planting_day = 90, 
                                  seuil = 11, K_pot=500, r_max = 0.07)
    # Store total population
    Nematode_df[, "total_pop"] <-rowSums(PopNem, na.rm = T)
    
    final_pop <- rbind(final_pop, Nematode_df[simulation_time,]%>%
                                    mutate(ln_1 = ln_1, lmax_3 = lmax_3)
                       )
  }
  
  #####    
      # We enrich the root system simulation data with metadata
      current_rootsystem <- current_rootsystem %>% 
                            mutate(ln_1 = ln_1, lmax_3 = lmax_3)
      
      # We create a table with all the root systems
      all_rootsystems <- rbind(all_rootsystems, current_rootsystem)
      
      # # We store the root system simulation with a unique name
      # write_csv(current_rootsystem, 
      #           paste0("outputs/rootsystems/rootsystem_",vp,
      #                  "_",vs,
      #                  "_",ln,
      #                  ".csv"))  
      
      # extract the root length density from the simulation data
      totlength <- data.frame(ln_1 = ln_1, lmax_3 = lmax_3,
                              simulation_id = n_cr_sim, 
                              total_length = sum(current_rootsystem$length), 
                              n_root = length(unique(current_rootsystem$branchID)))
      
      # We store in a data frame the rld from all the simulations
      all_totlength <- rbind(all_totlength, totlength)
  ###
  
  # plot Root and Nem
  print( plot_RV(RV)+ 
           ggtitle(paste0('RootVol (ln_1 = ',ln_1, ', lmax_3 = ',lmax_3,')'))  )
  print( plot_PopNem(PopNem, T) + 
           ggtitle(paste0('PopNem (ln_1 = ',ln_1, ', lmax_3 = ',lmax_3,')')) )
}

  print( plot_current_root_S(current_rootsystem) +
           ggtitle(paste0('Rootsystem (lmax_3 = ',lmax_3, ')') ) )
```

### Compare the rootsystem

```{r}

# final result :
final_pop$lmax_3 <- as.factor(final_pop$lmax_3)

### boxplot
ggplot(final_pop, aes(x=lmax_3, y=total_pop) ) + 
  geom_boxplot( fill="green", alpha=0.5)+ 
  ylab("Final nematode population") + xlab("Maximal length (cm)")
  
# Everything on the same plot
df <- melt(Nematode_df, id.vars="Time")
ggplot(df, aes(Time,value, col=variable)) + geom_point() +
        ylab("Nematode population [individuals]") + xlab("Time [days]")


all_totlength %>% 
  ggplot(aes(lmax_3, total_length, 
             colour = factor(ln_1))) +
  geom_line() + 
  theme_bw()

```


## Changing both `ln_1` and `lmax_3` 

```{r}
# Define param values
lmax3_vec <- c( 30 , 90 , 170 , 250)
ln1_vec <-  c( 1 , 1.6 ,  3.1 ,  4.6 )

# empty df for storing results
Nematode_df <- setNames(data.frame(matrix(ncol = 1, nrow = simulation_time)), 'Time')
Nematode_df['Time'] <- c(1:simulation_time)

final_pop <- NULL
all_rootsystems <- NULL
all_totlength <- NULL
n_tot_simulation <- length(lmax3_vec)  * length(ln1_vec)
n_cr_sim <- 0
n_rep <- 10

# initial population of nematode in each layer of soil
PopNem_init = c(20, 12, 10, 7, 1) # approx 50 nematodes in the beginning ~(Werf et al., 1986)

### loop over param ###
for (ln_1 in ln1_vec){
  for (lmax_3 in lmax3_vec){
    # Output the advancement in the simulation
    n_cr_sim <- n_cr_sim + 1
    print(paste0(n_cr_sim, " / ", n_tot_simulation, " crootbox sims :"))
        
    for(i in c(1:n_rep)){    
      print(paste0("                  || Rep - ", i))
      
      # assign new value to the param & run
      current_rootsystem <- launch_simulation2(lmax_3 = lmax_3, ln_1 = ln_1)
      
      # root volume
      RV <- root_volume(current_rootsystem, 250, 50)
      
      # model the nem. population
      PopNem <- Nematode_population(RV, modele, PopNem_init,  alpha = 0.015, planting_day = 90, 
                                    seuil = 11, K_pot=500, r_max = 0.07)
      # Store total population
      Nematode_df[, "total_pop"] <-rowSums(PopNem, na.rm = T)
      
      final_pop <- rbind(final_pop, Nematode_df[simulation_time,]%>%
                                      mutate(ln_1 = ln_1, lmax_3 = lmax_3)
                         )
    }
    
    #####    
        # We enrich the root system simulation data with metadata
        current_rootsystem <- current_rootsystem %>% 
                              mutate(ln_1 = ln_1, lmax_3 = lmax_3)
        
        # We create a table with all the root systems
        all_rootsystems <- rbind(all_rootsystems, current_rootsystem)
        
        # # We store the root system simulation with a unique name
        # write_csv(current_rootsystem, 
        #           paste0("outputs/rootsystems/rootsystem_",vp,
        #                  "_",vs,
        #                  "_",ln,
        #                  ".csv"))  
        
        # extract the root length density from the simulation data
        totlength <- data.frame(ln_1 = ln_1, lmax_3 = lmax_3,
                                simulation_id = n_cr_sim, 
                                total_length = sum(current_rootsystem$length), 
                                n_root = length(unique(current_rootsystem$branchID)))
        
        # We store in a data frame the rld from all the simulations
        all_totlength <- rbind(all_totlength, totlength)
    ###
    
    # plot Root and Nem
    # print( plot_RV(RV)+ 
    #          ggtitle(paste0('RootVol (ln_1 = ',ln_1, ', lmax_3 = ',lmax_3,')'))  )
    # print( plot_PopNem(PopNem, T) + 
    #          ggtitle(paste0('PopNem (ln_1 = ',ln_1, ', lmax_3 = ',lmax_3,')')) )
    # print( plot_current_root_S(current_rootsystem) + 
    #          ggtitle(paste0('Rootsystem (ln_1 = ',ln_1, ')') ) )
  }
}
#### End loop


```

### Compare the rootsystem

```{r}
# final result :
final_pop$lmax_3 <- as.factor(final_pop$lmax_3)
final_pop$ln_1 <- as.factor(final_pop$ln_1)

### boxplot
png("./fig/boxplot_final.png",width = 13, height = 8, res = 1000, units = "cm")

ggplot(final_pop, aes(fill=lmax_3, y=total_pop, x=ln_1 ) ) + 
  geom_boxplot(alpha=0.8)+ 
  ylab("Final nematode population") + xlab("Lateral density (cm)") +
  labs(fill="Maximum \nlength (cm)")
dev.off()
  
# Everything on the same plot
df <- melt(Nematode_df, id.vars="Time")
ggplot(df, aes(Time,value, col=variable)) + geom_point() +
        ylab("Nematode population [individuals]") + xlab("Time [days]")



all_totlength %>% 
  ggplot(aes(lmax_3, total_length, 
             colour = factor(ln_1))) +
  geom_line(size=1) + ylab("Total root length (cm)") + xlab("Maximal length - lmax (cm)")+
  labs(colour= "Lateral \ndensity (cm)")+
  theme_bw()

# Root system
all_rootsystems %>%
  ggplot() +
  theme_classic() +
  geom_segment(aes(x = x1, y = z1, xend = x2, yend = z2), alpha=0.9) +
  coord_fixed() +
  facet_grid(ln_1 ~ lmax_3)


```


